msuRACiFits_fits_rice

### 2025-05-12 CO2_response_fitting/Scripts/msuRACiFit_rice_params.Rmd
Add files via upload

---
title: "msuRACiFits_fits_rice_params"
author: "Supreeta Vijayakumar"
date: "`r Sys.Date()`"
output: html_document
---

@@

@@

```{r}
write.csv(Gstars_rice,file = "Outputs/Parameters/Gstars_rice.csv") #ppm
```

```{r}
write.csv(Gstars_Pa_rice,file = "Outputs/Parameters/Gstars_Pa_rice.csv") #Pa
```

@@

```{r}
msuRACiFit::genApp()
```

@@

### Import data for Kc_c and Kc_dHa:

```{r}
Kc_c <- 38.9
Kc_dHa <- 83.1
```

### Import data for Kcair_c and Kcair_dHa:

```{r}
Kcair_c <- 30.5 
Kcair_dHa <- 60.5
```

@@

```{r}
all_param$Ko<-(21000 / ((all_param$Kcair / all_param$Kc) - 1))/1000 
all_param$Temperature <- mean_temps 
all_param$Press <- mean_press 
write.csv(all_param,
         file = "Outputs/Parameters/fitComplete/Rice/kinetic_parameters_rice.csv")
```

@@

```{r}
for (k in seq_along(datasets)) {  
  data_k <- datasets[[k]]
  if ("data" %in% colnames(data_k)) {
    data_k <- data_k$data  
  }
  data_k <- as.data.frame(data_k)

@@

### Fit curves individually using fitComplete algorithm:

```{r}
completeFit1_rice <- fitComplete(A330502WT1, 
                                name_assimilation = "Photo", 
                                name_ci = "Ci", 
                                gammastar = Gstars_Pa_rice[1], 
                                O2 = 21, 
                                pressure = mean_press[1], 
                                tleaf = mean_temps[1], 
                                initialGuess = NA,
                                forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                ignoreTPU = F, 
                                maxiter = 500, 
                                Kc = all_param[1, "Kc"], 
                                Ko = all_param[1, "Ko"]) 
```

```{r}
completeFit2_rice <- fitComplete(A330502WT2, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[2], 
                                 O2 = 21, 
                                 pressure = mean_press[2], 
                                 tleaf = mean_temps[2], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA),
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, maxiter = 500, 
                                 Kc = all_param[2, "Kc"], 
                                 Ko = all_param[2, "Ko"]) 
```

```{r}
completeFit3_rice <- fitComplete(A330504WT1, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[3], 
                                 O2 = 21, 
                                 pressure = mean_press[3], 
                                 tleaf = mean_temps[3], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[3, "Kc"], 
                                 Ko = all_param[3, "Ko"]) 
```

```{r}
completeFit4_rice <- fitComplete(A330504WT2, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[4], 
                                 O2 = 21, 
                                 pressure = mean_press[4], 
                                 tleaf = mean_temps[4], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[4, "Kc"], 
                                 Ko = all_param[4, "Ko"]) 
```

```{r}
completeFit5_rice <- fitComplete(A330506WT1, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[5], 
                                 O2 = 21, 
                                 pressure = mean_press[5], 
                                 tleaf = mean_temps[5], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[5, "Kc"], 
                                 Ko = all_param[5, "Ko"])
```

```{r}
completeFit6_rice <- fitComplete(A330506WT2, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[6], 
                                 O2 = 21, 
                                 pressure = mean_press[6], 
                                 tleaf = mean_temps[6], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[6, "Kc"], 
                                 Ko = all_param[6, "Ko"]) 
```

```{r}
completeFit7_rice <- fitComplete(A330509WT1, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[7], 
                                 O2 = 21, 
                                 pressure = mean_press[7], 
                                 tleaf = mean_temps[7], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[7, "Kc"], 
                                 Ko = all_param[7, "Ko"]) 
```

```{r}
completeFit8_rice <- fitComplete(A330509WT2, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[8], 
                                 O2 = 21, pressure = mean_press[8], 
                                 tleaf = mean_temps[8], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[8, "Kc"], 
                                 Ko = all_param[8, "Ko"]) 
```

### Save parameter outputs:

```{r}
write.csv(completeFit1_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit1_console_rice_params.csv")

write.csv(completeFit2_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit2_console_rice_params.csv")

write.csv(completeFit3_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit3_console_rice_params.csv")

write.csv(completeFit4_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit4_console_rice_params.csv")

write.csv(completeFit5_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit5_console_rice_params.csv")

write.csv(completeFit6_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit6_console_rice_params.csv")

write.csv(completeFit7_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit7_console_rice_params.csv")

write.csv(completeFit8_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit8_console_rice_params.csv")
```

## Produce data tables for each curve:

```{r}
completeTables1_rice <- reconstituteTable(data=A330502WT1, 
                                          fitParams = completeFit1_rice[[1]],
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[1],
                                          O2=21, 
                                          pressure=mean_press[(1)], 
                                          tleaf = mean_temps[(1)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[1, "Kc"], 
                                          Ko=all_param[1, "Ko"])

completeTables2_rice <- reconstituteTable(data=A330502WT2, 
                                          fitParams = completeFit2_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[2], 
                                          O2=21, 
                                          pressure=mean_press[(2)], 
                                          tleaf = mean_temps[(2)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[2, "Kc"],
                                          Ko=all_param[2, "Ko"])

completeTables3_rice <- reconstituteTable(data=A330504WT1, 
                                          fitParams = completeFit3_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[3], 
                                          O2=21, 
                                          pressure=mean_press[(3)], 
                                          tleaf = mean_temps[(3)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[3, "Kc"], 
                                          Ko=all_param[3, "Ko"])

completeTables4_rice <- reconstituteTable(data=A330504WT2, 
                                          fitParams = completeFit4_rice[[1]], 
                                          name_assimilation = "Photo",
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[4], 
                                          O2=21, 
                                          pressure=mean_press[(4)], 
                                          tleaf = mean_temps[(4)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[4, "Kc"], 
                                          Ko=all_param[4, "Ko"])

completeTables5_rice <- reconstituteTable(data=A330506WT1, 
                                          fitParams = completeFit5_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[5], 
                                          O2=21, 
                                          pressure=mean_press[(5)], 
                                          tleaf = mean_temps[(5)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[5, "Kc"], 
                                          Ko=all_param[5, "Ko"])

completeTables6_rice <- reconstituteTable(data=A330506WT2, 
                                          fitParams = completeFit6_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[6], 
                                          O2=21, 
                                          pressure=mean_press[(6)], 
                                          tleaf = mean_temps[(6)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[6, "Kc"], 
                                          Ko=all_param[6, "Ko"])

completeTables7_rice <- reconstituteTable(data=A330509WT1, 
                                          fitParams = completeFit7_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[7], 
                                          O2=21, 
                                          pressure=mean_press[(7)], 
                                          tleaf = mean_temps[(7)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[7, "Kc"], 
                                          Ko=all_param[7, "Ko"])

completeTables8_rice <- reconstituteTable(data=A330509WT2, 
                                          fitParams = completeFit8_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[8], 
                                          O2=21, 
                                          pressure=mean_press[(8)], 
                                          tleaf = mean_temps[(8)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[8, "Kc"], 
                                          Ko=all_param[8, "Ko"])
```

@@

```{r}
write.csv(completeTables1_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit1_console_rice_dataTable.csv") 
write.csv(completeTables2_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit2_console_rice_dataTable.csv")
write.csv(completeTables3_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit3_console_rice_dataTable.csv") 
write.csv(completeTables4_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit4_console_rice_dataTable.csv")
write.csv(completeTables5_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit5_console_rice_dataTable.csv")
write.csv(completeTables6_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit6_console_rice_dataTable.csv") 
write.csv(completeTables7_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit7_console_rice_dataTable.csv")
write.csv(completeTables8_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit8_console_rice_dataTable.csv") 
```

### Plot graphs of limitations:

```{r}
completeGraph1_rice <- reconstituteGraph(data=A330502WT1, 
                                         fitParams = completeFit1_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[1], 
                                         O2=21, 
                                         pressure=mean_press[(1)], 
                                         tleaf=mean_temps[(1)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[1, "Kc"], 
                                         Ko=all_param[1, "Ko"])

completeGraph2_rice <- reconstituteGraph(data=A330502WT2, 
                                         fitParams = completeFit2_rice[[1]], 
                                         name_assimilation="Photo", name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[2], O2=21, 
                                         pressure=mean_press[(2)], tleaf=mean_temps[(2)], 
                                         ignoreTPU=F,
                                         Kc=all_param[2, "Kc"], 
                                         Ko=all_param[2, "Ko"])

completeGraph3_rice <- reconstituteGraph(data=A330504WT1, 
                                         fitParams = completeFit3_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[3], 
                                         O2=21, 
                                         pressure=mean_press[(3)], 
                                         tleaf=mean_temps[(3)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[3, "Kc"], 
                                         Ko=all_param[3, "Ko"])

completeGraph4_rice <- reconstituteGraph(data=A330504WT2, 
                                         fitParams = completeFit4_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[4],
                                         O2=21, 
                                         pressure=mean_press[(4)], 
                                         tleaf=mean_temps[(4)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[4, "Kc"], 
                                         Ko=all_param[4, "Ko"])

completeGraph5_rice <- reconstituteGraph(data=A330506WT1, 
                                         fitParams = completeFit5_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[5],
                                         O2=21, 
                                         pressure=mean_press[(5)], 
                                         tleaf=mean_temps[(5)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[5, "Kc"], 
                                         Ko=all_param[5, "Ko"])

completeGraph6_rice <- reconstituteGraph(data=A330506WT2, 
                                         fitParams = completeFit6_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[6],
                                         O2=21, 
                                         pressure=mean_press[(6)], 
                                         tleaf=mean_temps[(6)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[6, "Kc"], 
                                         Ko=all_param[6, "Ko"])

completeGraph7_rice <- reconstituteGraph(data=A330509WT1, 
                                         fitParams = completeFit7_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[7],
                                         O2=21, 
                                         pressure=mean_press[(7)], 
                                         tleaf=mean_temps[(7)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[7, "Kc"], 
                                         Ko=all_param[7, "Ko"])

completeGraph8_rice <- reconstituteGraph(data=A330509WT2, 
                                         fitParams = completeFit8_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[8],
                                         O2=21,
                                         pressure=mean_press[(8)], 
                                         tleaf=mean_temps[(8)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[8, "Kc"], 
                                         Ko=all_param[8, "Ko"]) 
```

### Save plots:

```{r}
png("Outputs/Graphs/fitComplete/Rice/completefits1_console_rice.png", width = 519, height = 457) 
plot(completeGraph1_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits2_console_rice.png", width = 519, height = 457) 
plot(completeGraph2_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits3_console_rice.png", width = 519, height = 457) 
plot(completeGraph3_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits4_console_rice.png", width = 519, height = 457) 
plot(completeGraph4_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits5_console_rice.png", width = 519, height = 457) 
plot(completeGraph5_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits6_console_rice.png", width = 519, height = 457) 
plot(completeGraph6_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits7_console_rice.png", width = 519, height = 457) 
plot(completeGraph7_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits8_console_rice.png", width = 519, height = 457) 
plot(completeGraph8_rice) 
dev.off()
```

#### Calculate sum of squared residuals:

```{r}
SSR1<-sum(completeTables1_rice$res^2)
SSR2<-sum(completeTables2_rice$res^2)
SSR3<-sum(completeTables3_rice$res^2)
SSR4<-sum(completeTables4_rice$res^2)
SSR5<-sum(completeTables5_rice$res^2)
SSR6<-sum(completeTables6_rice$res^2)
SSR7<-sum(completeTables7_rice$res^2)
SSR8<-sum(completeTables8_rice$res^2)
```

### Combine and save SSR values:

```{r}
SSR_values <- data.frame(SSR1,SSR2,SSR3,SSR4,SSR5,SSR6,SSR7,SSR8) 
write.csv(SSR_values, 
          file = "Outputs/Parameters/fitComplete/Rice/rice_console_SSR_values.csv", 
          row.names = FALSE)
```

### Export plot coordinates for limitations, example below:

```{r}
Ac<-completeGraph1_rice$plot_env$cdat 
Aj<-completeGraph1_rice$plot_env$jdat 
Ap<-completeGraph1_rice$plot_env$pdat 
limitations <- list(Ac,Aj,Ap)

write.csv(limitations,"Outputs/Tables/fitComplete/Rice/completeFit1_rice_limitations.csv")
```

>>>>

---
title: "msuRACiFits_fits_rice"
author: "Supreeta Vijayakumar"
date: "`r Sys.Date()`"
output: html_document
---

@@

### Specify an output directory:

```{r}
base_path <- here("Outputs", "Parameters")
```

@@

```{r}
Gstars_rice_file <- file.path(base_path, "Gstars_rice.csv")
write.csv(Gstars_rice,Gstars_rice_file) #ppm
```

```{r}
Gstars_Pa_rice_file <- file.path(base_path, "Gstars_Pa_rice.csv")
write.csv(Gstars_Pa_rice,Gstars_Pa_rice_file) #Pa
```

@@

```{r}
# msuRACiFit::genApp()
```

@@

### Import data for Kc_c and Kc_dHa (from Hermida-Carrera et al, 2016):

```{r}
Kc_c <- 38.9   # unitless
Kc_dHa <- 83.1 # kJ mol -1
```

### Import data for Kcair_c and Kcair_dHa from Hermida-Carrera et al, 2016:

```{r}
Kcair_c <- 30.5   # unitless
Kcair_dHa <- 60.5 # kJ mol -1
```

@@

```{r}
all_param$Ko<-(21000 / ((all_param$Kcair / all_param$Kc) - 1))/1000 
all_param$Temperature <- mean_temps 
all_param$Press <- mean_press

all_param_file <- file.path(base_path, "kinetic_parameters_rice.csv")
write.csv(all_param,all_param_file)
```

@@

```{r}
for (k in seq_along(datasets)) {  
  data_k <- datasets[[k]]
    if (hasName(data_k, "data")) {
    data_k <- data_k$data
  }
  data_k <- as.data.frame(data_k)

@@

## Save parameter outputs:

```{r}
for (o in seq_along(complete_Fits_rice_list)) {
  filename <- sprintf("completeFits_rice_params_%d.csv", o)
  output_filename <- file.path(base_path,filename)
  write.csv(complete_Fits_rice_list[[o]][[1]], 
            file = output_filename, 
            row.names = FALSE)
}
```

### Initialise an empty list to store table outputs and sums of squared residuals:

```{r}
complete_Tables_rice_list <- vector("list", length(datasets))
SSR <- numeric(length(complete_Tables_rice_list))
```

## Produce data tables using parameters fitted for each curve and the SSR assoaciated with each fit:

```{r}
    for (k in seq_along(datasets)) {  
    data_k <- datasets[[k]]
      if (hasName(data_k, "data")) {
      data_k <- data_k$data
    }
  data_k <- as.data.frame(data_k)

    complete_Tables_rice <- reconstituteTable(
    data = data_k,  
    fitParams = complete_Fits_rice_list[[k]][[1]],
    name_assimilation = "Photo",
    name_ci = "Ci",
    gammastar = Gstars_Pa_rice[k],
    O2 = 21,
    pressure=mean_press[(k)], 
    tleaf = mean_temps[(k)], 
    ignoreTPU=F, 
    Kc=all_param[k, "Kc"], 
    Ko=all_param[k, "Ko"])

  complete_Tables_rice_list[[k]] <- complete_Tables_rice
  SSR[k] <- sum(complete_Tables_rice_list[[k]]$`res^2`)
}
```

@@

```{r}
for (p in seq_along(complete_Tables_rice_list)) {
  filename <- sprintf("completeFits_rice_dataTable_%d.csv", p)
  output_filename <- file.path(base_path,filename)
  write.csv(complete_Tables_rice_list[[p]], 
            file = output_filename, 
            row.names = FALSE)
}
```

### Save SSR values:

```{r}
SSR_file <- file.path(base_path, "SSR_values_rice.csv")
write.csv(SSR,SSR_file)
```

### Initialise an empty list to store graph outputs:

```{r}
complete_Graphs_rice_list <- vector("list", length(datasets))
```

## Produce graphs of limitations using parameters fitted for each curve:

```{r}
    for (k in seq_along(datasets)) {  
    data_k <- datasets[[k]]
      if (hasName(data_k, "data")) {
      data_k <- data_k$data
    }
  data_k <- as.data.frame(data_k)

    complete_Graphs_rice <- reconstituteGraph(
    data = data_k,  
    fitParams = complete_Fits_rice_list[[k]][[1]],
    name_assimilation = "Photo",
    name_ci = "Ci",
    gammastar = Gstars_Pa_rice[k],
    O2 = 21,
    pressure=mean_press[(k)], 
    tleaf = mean_temps[(k)], 
    ignoreTPU=F, 
    Kc=all_param[k, "Kc"], 
    Ko=all_param[k, "Ko"])

  complete_Graphs_rice_list[[k]] <- complete_Graphs_rice
}
```

### Save graphs:

```{r}
for (p in seq_along(complete_Graphs_rice_list)) {
  filename <- sprintf("completefits_rice_Graph_%d.png", p)
  output_filename <- file.path(base_path, filename)

  png(output_filename, width = 519, height = 457)
  plot(complete_Graphs_rice_list[[p]])
  dev.off()
}
```

### Create output for limitation data:

```{r}
limitations_list <- vector("list", length(complete_Graphs_rice_list))
```

### Export plot coordinates for limitations:

```{r}
for (q in seq_along(complete_Graphs_rice_list)) {
  graph <- complete_Graphs_rice_list[[q]]
  Ac <- graph$plot_env$cdat
  Aj <- graph$plot_env$jdat
  Ap <- graph$plot_env$pdat

  limitations_list[[q]] <- list(Ac, Aj, Ap)
}
```

### Write limitations to output file:

```{r}
limitations_file <- file.path(base_path, "completeFit_rice_limitations.csv")
write.csv(limitations_list,limitations_file)
```
